How do changes in ex vary between countries?

### 2022-03-08 draft_paper.Rmd
add f test and stat sig indicator (is the p value < 0.05?)

compare_best_breakmodel_with_null %>% 
  mutate(
    aic_alt  = map_dbl(model_alt, AIC),
    aic_null = map_dbl(model_null, AIC)
  ) %>% 
  mutate(
    alt_preferred = map2_lgl(aic_alt, aic_null, ~ifelse(.x < .y, TRUE, FALSE))
  )

>>>>

compare_best_breakmodel_with_null %>% 
  mutate(
    aic_alt  = map_dbl(model_alt, AIC),
    aic_null = map_dbl(model_null, AIC)
  ) %>% 
  mutate(
    alt_preferred = map2_lgl(aic_alt, aic_null, ~ifelse(.x < .y, TRUE, FALSE))
  ) %>% 
  mutate(
    anova_results = map2(model_alt, model_null, anova)
  ) %>% 
  mutate(
    ftest_pval = map_dbl(anova_results, ~.[2,6]),
    stat_sig_preference = ftest_pval < 0.05
  )
